---
title: "Statistics-for-Business-Regression"
author: "Adelia Januarto"
output-file: html
---


# Introduction

# Dataset 1

```{r, warning=F, message=F}
library(tidyverse)
```

The happiness world report dataset was taken from [UCI Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/Heart+failure+clinical+records).

```{r}
# import dataset
df <- 
  read_csv("datasets/heart_failure_clinical_records.csv", 
           show_col_types = F)

# display top-10 rows
df[1:10,]
```

Description:
- `age`: the patient's age (in years)
- `anemia`: anemia status
- `high_blood_pressure`: hypertension status
- `creatinine_phosphokinase`: level of CPK enzyme in blood (mcg/L)
- `diabetes`: diabetes status
- `ejection_fraction`
- `platelets`
- `sex`
- `creatinine_phosphokinase`
- `serum sodium`
- `smoking`
- `death_event`

# Dataset 2
Source: https://www.kaggle.com/datasets/kumarajarshi/life-expectancy-who
```{r}
# import dataset
df_2 <- 
  read_csv("datasets/life-expectancy.csv",
           show_col_types = F)

# show top rows
df_2 %>%
  rename("LifeExpectancy" = "Life expectancy",
         "AdultMortality" = "Adult Mortality",
         "InfantMortality" = "infant deaths",
         "IncomeCompositionofResource" = "Income composition of resources")
```

```{r}
# check missing values per col
na_table <- 
  df_2 %>%
  is.na() %>%
  colSums() %>%
  data.frame() 

colnames(na_table)[1] <- "count"
na_table
```

```{r}
# check duplicates
df_2 %>%
  duplicated() %>%
  sum()
```

```{r}
# automate EDA
library(dataMaid)
library(ExPanDaR)
library(DataExplorer)
library(dlookr)
```


```{r}
create_report(df_2)
```

```{r}
makeDataReport(df_2, output = "html")
```

```{r}
eda_web_report(df_2,output_format = "html")
```
-   Correlation plot: https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html 

-   Same: https://statsandr.com/blog/correlation-coefficient-and-correlation-test-in-r/

